%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Jyothi Prakash Sangaraju} \\ \vspace{1pt}
    Wichita, Kansas - 67208\\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ 316-293-8584 ~ \href{mailto:prakashsangaraju09@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{prakashsangaraju09@gmail.com}} ~ 
    \href{https://linkedin.com/in/jyothi-prakash-sangaraju-20b2b226a}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/jyothi-prakash-sangaraju-20b2b226a}}  ~
    \vspace{-8pt}
\end{center}


%--------PROFESSIONAL SUMMARY---------
\section{Professional Summary}
\small{
Data Engineer and Data Analyst with 3+ years of experience in ETL/ELT pipeline development, data warehousing, and business intelligence. Demonstrated expertise in Python, SQL, AWS, and Azure with proven success optimizing database performance by 65\%, implementing data quality frameworks reducing errors by 65\%, and delivering analytics solutions that generated \$1.2M in cost savings.
}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Wichita State University}{Sep 2022 -- May 2024}
      {Master of Science in Computer Science}{Wichita, Kansas}
  \resumeSubHeadingListEnd
  \resumeSubHeadingListStart
    \resumeSubheading
      {Siddhartha Institute of Engineering and Technology}{Aug 2017 -- May 2021}
    {Bachelor's degree in Electronics and Communication Engineering}{Puttur, Andhra Pradesh}
  \resumeSubHeadingListEnd


%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming Languages}{: Python, SQL, PySpark, Pandas, NumPy} \\
     \textbf{Database Technologies}{: PostgreSQL, MySQL, MongoDB, Snowflake, SQL Server} \\
     \textbf{ETL/ELT Tools}{: Apache Airflow, Apache Spark, Azure Data Factory} \\
     \textbf{Cloud Platforms}{: Amazon Web Services (S3, Redshift, Glue), Microsoft Azure, Google Cloud Platform} \\
     \textbf{Business Intelligence}{: Tableau, Microsoft Power BI, Data Visualization, Dashboard Development} \\
     \textbf{Development Tools}{: Git, GitHub, Docker, Jupyter Notebook, Visual Studio, Team Foundation Server}
    }}
 \end{itemize}
 \vspace{-10pt}


%-----------EXPERIENCE-----------
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Data Engineer}{July 2023 -- December 2023}
      {Pfizer Inc. - Aseptic Area Entrance Management (AAEM)}{Pea Pack, NJ}
      \resumeItemListStart
        \resumeItem{Developed ETL pipelines using Python, PySpark, Apache Airflow, and Azure Data Factory for data integration, successfully integrating multiple data sources from security, environmental monitoring, and training systems.}
        \resumeItem{Designed cloud-based data warehousing solutions using AWS (S3, Redshift, Glue), Snowflake, and SQL Server to optimize data processing and reporting.}
        \resumeItem{Implemented real-time data streaming with Apache Spark for workflow automation and built automated data validation frameworks using SQL, Pandas, and NumPy to ensure data quality.}
        \resumeItem{Created interactive dashboards with Tableau and Power BI for data visualization and reporting while ensuring data governance and compliance by collaborating with cross-functional teams.}
      \resumeItemListEnd

    \resumeSubheading
      {Junior Data Engineer}{May 2021 -- December 2022}
      {TATA Consultancy Services.inc}{Bengaluru}
      \resumeItemListStart
        \resumeItem{Engineered data pipelines processing 1M+ daily records with 99.9\% accuracy using Python and SQL.}
        \resumeItem{Developed interactive business intelligence dashboards using Tableau and Power BI that reduced decision-making time by 40\%.}
        \resumeItem{Built automated data quality monitoring system using Python that improved data reliability by 35\%.}
        \resumeItem{Led cross-functional data analytics initiatives resulting in \$1.2M cost savings through process optimization and created SQL-based data models to support complex business reporting requirements across multiple departments.}
      \resumeItemListEnd

    \resumeSubheading
      {Data Analyst}{November 2019 -- April 2021}
      {Tech Mahindra}{Location}
      \resumeItemListStart
        \resumeItem{Built and maintained ETL pipelines for extracting, transforming, and loading data from 12+ source systems.}
        \resumeItem{Designed database schemas and dimensional data models in PostgreSQL and MySQL.}
        \resumeItem{Supported migration of on-premises data infrastructure to AWS cloud services, reducing storage costs by 30\%.}
        \resumeItem{Automated data quality verification processes using Python scripts, reducing manual effort by 40\%.}
      \resumeItemListEnd
    
  \resumeSubHeadingListEnd
\vspace{-10pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Weather Data Collection and Storage Pipeline} $|$ \emph{Apache Airflow, Python, PostgreSQL}}{January 2023 -- April 2023}
          \resumeItemListStart
            \resumeItem{Designed and implemented an ETL pipeline that retrieves weather data from the Open-Meteo API for London, processes it, and stores it in a PostgreSQL database using Apache Airflow for orchestration.}
            \resumeItem{Developed modular ETL steps using task decorators for extract (fetching API data with HttpHook), transform (processing raw data), and load (storing in database) operations.}
            \resumeItem{Implemented automatic table creation, connection management for database and API credentials, error handling for data validation, and time series collection with timestamps.}
          \resumeItemListEnd
          \vspace{-5pt}
      \resumeProjectHeading
          {\textbf{Real-time Retail Analytics Platform} $|$ \emph{Apache Kafka, Apache Spark, AWS Redshift, Apache Airflow}}{Jan 2024 - April 2024}
          \resumeItemListStart
            \resumeItem{Designed end-to-end data architecture using Apache Kafka, Apache Spark, and AWS Redshift for real-time retail analytics.}
            \resumeItem{Implemented automated ETL workflows with Apache Airflow for scheduling and monitoring data processing tasks.}
            \resumeItem{Created real-time dashboards for inventory tracking and analysis, resulting in 25\% inventory turnover improvement.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-10pt}

%-----------CERTIFICATIONS-----------
\section{Certifications}
    \resumeItemListStart
        \resumeItem{AWS Certified Solutions Architecture Job Simulation}
        \resumeItem{Data Visualisation: Empowering Business with Effective Insights - TATA Consultancy Services}
        \resumeItem{Python Programming, SQL Database Language- Qspiders}
    \resumeItemListEnd

\end{document}